brados: declarative, programmable object storage

### 2016-05-25 paper.tex
claros update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

As Ceph continues to develop into a target for building distributed services
and applications, it is important to not restrict use to developers seasonsed
in distributed programming and those with knowledge of the intracacies of Ceph
and its performance model. To this end we present Brados, a declarative language with
relational semantics for defining the behavior of RADOS object interfaces.
Brados uses a simple declarative data model, can reduce the learning curve
for new users, and allows existing developers to increase productivity by
writing less code that is more portable.

The Brados language corresponds to a subset of the Bloom language, and models the
storage system state uniformly as a collection of
relations~\cite{alvaro:cidr11}. The composition of a collection of existing
interfaces is then expressed as a collection of high-level \emph{queries} that
describe how a stream of requests (API calls) are filtered, transformed and
combined with existing state to define streams of outputs (API call returns as
well as updates to system state).  Separating the relational semantics of such
compositions from details of their physical implementations introduces a
number of degrees of freedom, similar to the ``data independence'' offered by
database query languages.  The choice of access methods (for example, whether
to use a bytestream interface or a key/value store), storage device
classes (e.g., whether to use HDDs or SDDs), physical layout details (e.g. a
1:1 or N:1 mapping) and execution plans (e.g. operator ordering) can be
postponed to execution time.  The optimal choices for these physical design
details are likely to change much more often than the logical specification,
freeing the interface designer from the need to rewrite systems and device and
interface characteristics change.

@@

>>>>

As Ceph continues to develop into a target for building distributed services
and applications, it is important to not restrict use to developers seasonsed
in distributed programming and those with knowledge of the intracacies of Ceph
and its performance model. The hard-coded imperative method of writing object
interfaces today restrict the optimizations that can be performed
automatically or derived from static analysis.  To this end we present Brados,
a declarative language with relational semantics for defining the behavior of
RADOS object interfaces.  Brados uses a declarative data model, can reduce the
learning curve for new users, and allows existing developers to increase
productivity by writing less code that is more portable.

The Brados language corresponds to a subset of the Bloom language which a
declarative language for expressing distributed programs as an unordered set
of rules. These rules fully specify program semantics and allow a programmer
to ignore the details associated with how a program is evaluated. This level
of abstraction is attractive for building storage interfaces whose portability
and correctness is critical.

@@

Brados models the storage system state uniformly as a collection of
relations~\cite{alvaro:cidr11}. The composition of a collection of existing
interfaces is then expressed as a collection of high-level \emph{queries} that
describe how a stream of requests (API calls) are filtered, transformed and
combined with existing state to define streams of outputs (API call returns as
well as updates to system state).  Separating the relational semantics of such
compositions from details of their physical implementations introduces a
number of degrees of freedom, similar to the ``data independence'' offered by
database query languages.  The choice of access methods (for example, whether
to use a bytestream interface or a key/value store), storage device classes
(e.g., whether to use HDDs or SDDs), physical layout details (e.g. a 1:1 or
N:1 mapping) and execution plans (e.g. operator ordering) can be postponed to
execution time.  The optimal choices for these physical design details are
likely to change much more often than the logical specification, freeing the
interface designer from the need to rewrite systems and device and interface
characteristics change.
